% resume.tex
% vim:set ft=tex spell:

\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{enumitem}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% Links
\usepackage{hyperref}
\hypersetup{
    colorlinks=false,
    }

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Blake Abel}}

\href{mailto:blakecabel@gmail.com}{blakecabel@gmail.com}\ \ \textbullet \ \ \href{tel:314-800-7794}{(314)-800-7794}\ \ \textbullet \ \ \href{https://github.com/blabel3}{github.com/blabel3}\ \ \textbullet \ \ \href{https://www.linkedin.com/in/blabel3/}{linkedin.com/in/blabel3/}

\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
	\parskip=0.1em

	\item 
	\headerrow
		{\textbf{Boston University - Computer Science Major}}
		{\textbf{Boston, MA}}
	\\
	\headerrow
		{\emph{College of Arts \& Sciences, Kilachand Honors College}}
		{\emph{2018 -- Jan 2022}}
	
	\begin{itemize*}
		\item Relevant Coursework: AI, Data Science, Discrete Mathematics, Number Theory, Algorithms,
		Computer Systems, Computer Networks, Linear Algebra, Functional Programming
	\end{itemize*}

\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Work Experience}

\begin{itemize}
	\parskip=0.1em
	
	\item
	\headerrow
		{\textbf{Microsoft}}
		{\textbf{Boston, MA}}
	\\
	\headerrow
		{\emph{Power Platform Software Engineer Intern}}
		{\emph{2021}}
	\begin{itemize*}
		\item Architected a new feature for the Power Platform Admin Center, and designed an in-depth spec to share with the team and to guide development during the internship.
		\item Created and deployed database tables to support the new feature alongside existing tables.
		\item Built an API to handle requests for the new feature, and the documentation so other groups at Microsoft could effectively build app integrations using it.
	    \item Integrated into a team of FTEs and learned from people throughout the company.
	\end{itemize*}
	
	\item
	\headerrow
		{\textbf{Microsoft}}
		{\textbf{Boston, MA}}
	\\
	\headerrow
		{\emph{Garage Software Engineer Intern}}
		{\emph{2020}}
	\begin{itemize*}
		\item Created a project for the Microsoft Teams platform sponsored by the Microsoft Casual Gaming team, from planning to release working alongside other Garage interns.\
		\item Revamped an old codebase to create a more efficient modern game that used web technologies to handle multiple players in a Teams chat.
		\item Presented to stakeholders such as the sponsor team CTOs at Microsoft regularly.
	\end{itemize*}
	
	\item
	\headerrow
		{\textbf{Dow Jones}}
		{\textbf{New York, NY}}
	\\
	\headerrow
		{\emph{Web Development Internship @ Barrons.com}}
		{\emph{2019}}
	\begin{itemize*}
		\item Sped up site load times by 37\% by optimizing their image loading. 
		\item Created a project called Snapshots by myself that automatically captures a screenshot of each Dow Jones owned page and saves it along with the pages' code to an AWS storage bucket.
		\item Presented Snapshots to the CTO and other tech leads at the company, including a demo.
	\end{itemize*}
	
	\item
	\headerrow
		{\textbf{BU SPARK!}}
		{\textbf{Boston, MA}}
	\\
	\headerrow
		{\emph{Special Initiatives Intern}}
		{\emph{2019}}
	\begin{itemize*}
		\item Worked on an innovative project that aims to analyze the health of open source projects and the communities around them with diversity and inclusion metrics.
	\end{itemize*}
	

\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Projects}

\begin{itemize}
	\parskip=0.1em
	
	\item \textbf{WTBU-Radio:}
		Cross-platform (React Native) iOS and Android app for listening to the BU radio station live stream \& archived broadcasts natively. Released on Android and iOS app stores.
	
	\item \textbf{E-Mission:}
		Won WHACK for Best MassCEC Project and Best Use of Google Cloud API: Android app that shows users their monetary/carbon savings by switching to electric cars based on their driving. 
	
\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Skills}

\begin{itemize}
	\parskip=0.1em

	\item \textbf{Languages:} Typescript, Python, Java, C\#, HTML/CSS \
	\textbullet \textbf{Tools:} CLI, Git, Slack, Jira, Azure DevOps
	
\end{itemize}

\end{document}
